An Optimized Agent for Capture The Flag Pac-Man

### 2011-03-09 projectWriteup/paper.tex

\begin{document}
\maketitle
\section{Introduction}
A popular and relevant field in artificial intelligence is noisy gameplay
\cite{miik}.  One fun example of this field is Capture the Flag (CTF)
Pac-Man.  In this paper, we discuss our implementation of an optimized, flexible agent to play CTF Pac-Man.

@@

\section{Heuristics}
We thought much more about our choice of heuristics than about their weights, relying instead on automated techniques to choose optimal parameters.  Our choice of heuristics was primarily driven by attempting to think about things in ways similar to humans; in each ``mode" we evaluated the position using heuristics relevant to examining the board from the perspective of the human strategy.

@@

\subsection{Defense}
The defensive heuristics that we found most helpful were staying close to our enemies, getting them into single-exit (trapped) scenarios and ensuring that for any piece of food we were closer than our opponents.  A key limitation that we had was that losing sight of attacking enemies could be very dangerous because mutual lack of information is very helpful to attackers.  However, because we were able to deduce an exact location any time food went missing, any agent that was doing serious harm was inherently easy to track.
\subsection{Hold the Line}
Playing defense against agents who had not crossed onto our side was a very different problem than playing it against agents who had, mostly because trying to eat them was no longer a strong strategy.  Hence we hit upon the idea of separating that type of play into a ``Hold The Line" heuristic.  For the purposes of holding the line, our agents would ``match up'' against usually one but sometimes more opposing agents depending on whether we had some agents attacking.  Our agents mirror their moves, trying to stay closer to all of the squares on the border than the opponents that that agent was ``covering''.  With good inference, as is possible in a 6 agent game, it could become very hard for any opposing agents to cross the border.

>>>>

\begin{document}
\maketitle
\section{Introduction}
A popular and relevant field in artificial intelligence is noisy gameplay\cite{miik}.  One fun example of this field is Capture the Flag (CTF)
Pac-Man.  In this paper, we discuss our implementation of an optimized, flexible agent to play CTF Pac-Man.

@@

\section{Heuristics}
We thought much more about our choice of heuristics than about their weights, relying instead on automated techniques to choose optimal parameters.  Our choice of heuristics was primarily driven by attempting to think about things in ways similar to humans; in each "mode" - offense, defense, and hold the line - we evaluated the positions using heuristics relevant to examining the board from the perspective of the human strategy.

@@

\subsection{Defense}
The defensive heuristics that we found most helpful were staying close to our enemies, getting them into single-exit (trapped) scenarios and ensuring that for any piece of food we were closer than our opponents.  A key limitation that we had was that losing sight of attacking enemies could be very dangerous because mutual lack of information is very helpful to attackers.  However, because we were able to deduce an exact location any time food went missing, any agent that was doing serious harm was inherently easy to track.

\subsection{Hold the Line}
Playing defense against agents who had not crossed onto our side was a very different problem than playing it against agents who had, mostly because trying to eat them was no longer a strong strategy.  Hence we hit upon the idea of separating that type of play into a ``Hold The Line" heuristic.  For the purposes of holding the line, our agents would ``match up'' against usually one but sometimes more opposing agents depending on whether we had some agents attacking.  Our agents mirror their moves, trying to stay closer to all of the squares on the border than the opponents that that agent was ``covering''.  With good inference, as is possible in a 6 agent game, it could become very hard for any opposing agents to cross the border.
